---
title: "Storm analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(results = FALSE)

require(dplyr)
require(ggplot2)
require(lubridate)

```

# Summary
The goal of this analysis is to define answers for 2 basic questions:  
- Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?  
- Across the United States, which types of events have the greatest economic consequences?  
  
The analysis is based on the information collected by the National Weather Service, published [here](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2).  
  
```{r download and prepare data}
sLink <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
fName <- "StormData.csv.bz2"
if ( !file.exists( "fName" ) ){ download.file( sLink,fName ) }
if ( !exists ("dsSource" ) ){ dsSource <- read.csv(fName) }

dsSource$BGN_DATE <- mdy_hms( dsSource$BGN_DATE )
dsSource$Year <- as.factor( year( dsSource$BGN_DATE ) )

ds <- dsSource[,c("Year","STATE","EVTYPE","FATALITIES","INJURIES")]

```

## The most harmful with respect to population health storms
