---
title: "Storms analysis"
author: "Grigory Sharkov"
date: "4 janvier 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(lubridate)
library(stringdist)

library(tm)  # for text mining
library(SnowballC) # for text stemming
library(wordcloud) # word-cloud generator 
library(RColorBrewer) # color palettes
```

## Introduction

Storms and other severe weather events can cause both public health and economic problems for communities and municipalities. Many severe events can result in fatalities, injuries, and property damage, and preventing such outcomes to the extent possible is a key concern.
This project involves exploring the U.S. National Oceanic and Atmospheric Administration's (NOAA) storm database. This database tracks characteristics of major storms and weather events in the United States, including when and where they occur, as well as estimates of any fatalities, injuries, and property damage.


## Questions
This data analysis  addresses the following questions:  
1. Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?  
2. Across the United States, which types of events have the greatest economic consequences?  

### Which types of events are most harmful with respect to population health?
```{r preparations echo=FALSE}
strSource <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
strName <- "data.csv.bz2"
if ( !file.exists(strName) ){
  download.file(strSource,strName)
}

if ( !exists(dsSource) ){
  dsSource <- read.csv(strName)
} 

ds <- dsSource[!is.na(dsSource$BGN_DATE),c("BGN_DATE","EVTYPE","FATALITIES","INJURIES")]
ds$BGN_DATE <- as.Date(ds$BGN_DATE,format = "%m/%d/%Y")
ds$YEAR <- year(ds$BGN_DATE)

#it seems there are too many event types. Let's try reducing it
dsEvents <- read.csv2("dsEvents.csv")
dsTemp <- merge(ds,dsEvents, by.x = "EVTYPE",by.y = "Event", all.x = T)

```

It seems that we have too many event types
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
